A Methodology to Define QoS and SLA Requirements in Service Choreographies

### 2012-08-07 articles/CAMAD2102/article-version2.tex
Adding HP-Baile and CHOReOS sponsors

\section*{Acknowledgment}

 This work is supported by the European Community's Seventh Framework Programme FP7/2007-2013 under grant agreement number
257178 (project CHOReOS - Large Scale Choreographies for the Future Internet - \url{www.choreos.eu}).

>>>>

\section*{Acknowledgment}
This work is supported by HP Brasil under technical cooperation agreement number HP-045/12 (Baile Project - \url{http://ccsl.ime.usp.br/baile/}) 
and the European Community's Seventh Framework Programme FP7/2007-2013 under grant agreement number 257178 (Project CHOReOS - Large Scale 
Choreographies for the Future Internet - \url{http://www.choreos.eu}).

% This work is supported by the European Community's Seventh Framework Programme FP7/2007-2013 under grant agreement number
%257178 (project CHOReOS - Large Scale Choreographies for the Future Internet - \url{www.choreos.eu}).
